Modeling vertical-axis cross-flow turbine wakes

### 2015-07-24 paper.tex
Correct spelling of snappyHexMesh
Add statement about vertical wake recovery

@@

Meshes were generated using \textit{OpenFOAM}'s \textit{blockMesh} and
\textit{snappHexMesh} utilities. Mesh topology consists of a background
hexahedral mesh, which is refined in all three directions by a factor of 2 in a
rectangular region containing the turbine and near-wake (0.9 m upstream, 1.3 m
downstream, $\pm 0.9$ m cross-stream, and $\pm 0.8$ m vertically). Cells
adjacent to the turbine shaft and struts are refined by a factor of 4, while
cells adjacent to the blades are refined by a factor of 6. To capture the
boundary layer, 20 layers are added next to the blades with an expansion ratio
of 1.2. Overall mesh refinement is controlled by a single parameter---the number
of cells in the streamwise direction, $N_x$.

>>>>

It has been shown that the momentum and energy transport processes in the
near-wake of a high-solidity, low aspect ratio vertical-axis turbine are
dominated by vertical advection \cite{Bachant2015-JoT}. It logically follows
that a 2-D simulation would not correctly predict wake recovery, but is of
interest to what extent this is true, since the computational feasibility of 2-D
simulations is attractive.

@@

Meshes were generated using \textit{OpenFOAM}'s \textit{blockMesh} and
\textit{snappyHexMesh} utilities. Mesh topology consists of a background
hexahedral mesh, which is refined in all three directions by a factor of 2 in a
rectangular region containing the turbine and near-wake (0.9 m upstream, 1.3 m
downstream, $\pm 0.9$ m cross-stream, and $\pm 0.8$ m vertically). Cells
adjacent to the turbine shaft and struts are refined by a factor of 4, while
cells adjacent to the blades are refined by a factor of 6. To capture the
boundary layer, 20 layers are added next to the blades with an expansion ratio
of 1.2. Overall mesh refinement is controlled by a single parameter---the number
of cells in the streamwise direction, $N_x$.
